Why robot programming is hard

### 2013-12-02 paper.tex
Revision complete, sending for Steve's approval

% Feedback from Matei:

% Make assumptions more explicit in intro
% Robot use == robot programming
% Differentiate end user programming from roboticist programming
% Teach/instruct/tell == programming

% Non-quantitative Henry statistics

% Cartesian robot control is a solved problem

@@

One way to trade off expressiveness for simplicity is to abstract away details of robot behavior into higher-level primitives. This abstraction can be difficult for roboticists to accept, who have become accustomed to having fine-grained control over robot behavior and error handling. Yet abstracting away these details is going to be critical for end users to be able to develop a working understanding of the robot's functionality.

@@

The drawback of this interface was that the user lost fine-grained control over exactly how the robot performed these tasks. For example, the interface only supported using the robot's right arm to pick up an object; the left arm was unused. It did not allow the user to specify exactly how to pick up an object (e.g. from above or from the side), even though these parameters can be customized at a lower level of control. The challenge in designing a simpler interface is to carefully craft exactly which functionality to expose, and which functionality can be safely hidden from casual users.

@@

@@

Finally, video gaming technology is driving a new crop of input and output devices that make it easier to interact with and perceive the 3D world around us. These devices will make it easier for robots to perceive the world in three dimensions, and for people to instruct those robots using more natural gestures. Input devices such as the Razer Hydra, Leap Motion Controller, and Microsoft Kinect can sense motion in 3D, enabling computers to sense motion and objects in the world. 3D output devices such as the Oculus Rift project stereo images in 3D so that people can perceive what robots are seeing in three dimensions.

These new devices could enable a new generation of robot control interfaces that make interacting with robots more natural and intuitive.

@@

Personal service robots have an enormous potential to do good for humanity by enabling people to live more independently. However, controlling these robots boils down to a small matter of programming. In this article I have explained why programming robots is inherently difficult, even for skilled programmers.  Drawing lessons from the field of end user programming, we have proposed several paths forward that may enable the creation of more accessible interfaces for personal robots in the future.
\end{changebar}

>>>>

@@

One way to trade off expressiveness for simplicity is to abstract away details of robot behavior into higher-level primitives. This abstraction can be difficult for roboticists to accept, who have become accustomed to having fine-grained control over robot behavior and error handling. Yet abstracting away these details is going to be critical for end users to be able to develop a working understanding of a robot's functionality.

@@

The drawback of this interface was that the user lost fine-grained control over exactly how the robot performed these tasks. For example, the interface only supported using the robot's right arm to pick up an object; the left arm was unused. It did not allow the user to specify exactly how to pick up an object (e.g. from above or from the side), even though these parameters can be customized at a lower level of control.

The challenge in designing a simpler interface is to carefully craft exactly which functionality to expose, and which functionality can be safely hidden from casual users.  For the intended users of the Continuous Ops interface, the provided functionality was sufficient and satisfied the requirements of being easy to use and always available. In fact, we heard of several cases where people used the interface remotely (e.g. while away at a conference) to show off the functionality of the robots in the lab.

@@

\begin{changebar}
This approach worked well during a multi-day deployment of a delivery system at Willow Garage. Users could request delivery of chocolates or snacks to their office, and the system would autonomously retrieve those items and deliver them to their office door. In the rare cases that the autonomous behaviors failed, several roboticists were notified by email and played the role of teleoperators. They initiated recovery behaviors to get the robots back on track. From the end users' perspective, the robot performed its tasks fully autonomously, sparing them from having to worry about specifying recovery behaviors.
\end{changebar}

@@

Finally, video gaming technology is driving a new crop of input and output devices that make it easier to interact with and perceive the 3D world around us. These devices will make it easier for robots to perceive the world in three dimensions, and for people to instruct those robots using more natural gestures. Input devices such as the Razer Hydra, Leap Motion Controller, and Microsoft Kinect can sense motion in 3D, enabling robots to better sense motion and objects in the world. 3D output devices such as the Oculus Rift project stereo images in 3D so that people can perceive what robots are seeing in three dimensions.

These new devices could enable a new generation of robot control interfaces that make interacting with robots more natural and intuitive. For example, David Gossow at Willow Garage developed a research prototype called the PR-2 Surrogate which provided a fully-immersive teleoperation interface for the PR-2 robot. It used a Razer Hydra control to track your hand positions, which were then mapped directly to the robot's hand positions. It also displayed a stereo camera feed from the robot's head-mounted cameras into an Oculus Rift device, giving you a stereo view of what the robot was seeing. The Rift's head tracking capability was mapped to moving the robot's head, enabling you to look around the robot's environment just by turning your head. This demo showed that these new input/output technologies hold much promise for making it easier to interact with, control, and program complex robots.

@@

Personal service robots have an enormous potential to do good for humanity by enabling people to live more independent lives and free them from mundane housekeeping chores. However, controlling these robots boils down to a small matter of programming. In this article I have explained why programming robots is inherently difficult, even for skilled programmers.  Drawing lessons from the field of end user programming, I have proposed several paths forward that may enable the creation of more accessible interfaces for personal robots in the future.
\end{changebar}
